Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-15 analysis/paper/paper.Rmd
Remove sentence describing work that wasn't done.

A custom function, `import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2022].
Values for software packages were checked for spelling consistency and corrections were made manually where necessary.
When working with these data in R, all strings of software character values were converted to fully upper-case to standardise the capitalisation and alleviate any issues with capitalisation used between evaluators.
In some cases the `software_avail`, or the openness of the software used, score did not agree with the software that was recorded and the agreed-upon criteria, so these scores were modified after discussion to match the ratings to the record of the software that was used in each respective paper.
For example, a paper was rated as having a `software_avail` rating of `3`, but the evaluator noted that Excel had been used; here, the `software_avail` rating was changed to `2` to bring it into line with the agreed upon guidelines.
In other cases, papers did not adequately describe all the software used, e.g., GenAlEx, an Excel add-on, was referred to but Excel was not mentioned in the text.
Here, Excel was added to the `software_used` column and the `software_avail` score was adjusted accordingly.
The software availability, computational methods availability and data availability scores were converted from 0 -- 3 to 1 -- 4 ordinal score values for analysis.

@@

The statistical analysis was performed using R version `r version$version.string` [@RCT2022] on an Apple MacBook Pro (13-inch, M1, 2020).

>>>>

A custom function, `import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2022].
Values for software packages were checked for spelling consistency and corrections were made manually where necessary.
When working with these data in R, all strings of software character values were converted to fully upper-case to standardise the capitalisation and alleviate any issues with capitalisation used between evaluators.
In some cases the `software_avail`, or the openness of the software used, score did not agree with the software that was recorded and the agreed-upon criteria, so these scores were modified after discussion to match the ratings to the record of the software that was used in each respective paper.
For example, a paper was rated as having a `software_avail` rating of `3`, but the evaluator noted that Excel had been used; here, the `software_avail` rating was changed to `2` to bring it into line with the agreed upon guidelines.
In other cases, papers did not adequately describe all the software used, e.g., GenAlEx, an Excel add-on, was referred to but Excel was not mentioned in the text.
Here, Excel was added to the `software_used` column and the `software_avail` score was adjusted accordingly.

@@

The statistical analysis was performed using R version `r version$version.string` [@RCT2022] on an Apple MacBook Pro (13-inch, M1, 2020).
Statistical analysis were carried out using R 4.1.0 (R Core Team, 2021), the rstanarm (v2.13.1; Gabry & Goodrich, 2016) and the report (v0.2.0; Makowski, Patil, & Lüdecke, 2019) packages. The full reproducible code is available in Supplementary Materials.
